\begin{frame}
    \frametitle{Why should you care?}

    How you connect matters. Running and synchronising \textbf{your own instance} ---
    rather than only querying the shared one --- buys you real advantages.

    \vspace{0.5em}

    \begin{center}
        \begin{columns}[T]
            \begin{column}{0.5\textwidth}
                \card{\linewidth}{1.5em}{\faUserSecret \, \textbf{Confidentiality}}
                    {Your searches can be very sensitive}
            \end{column}
            \hfill
            \begin{column}{0.5\textwidth}
                \card{\linewidth}{1.5em}{\faBolt \, \textbf{Availability}}
                    {Don't depend on shared performance}
            \end{column}
        \end{columns}
        \begin{columns}[T]
            \begin{column}{0.5\textwidth}
                \card{\linewidth}{1.5em}{\faTools \, \textbf{Capability}}
                    {Host / admin-only features}
            \end{column}
            \hfill
            \begin{column}{0.5\textwidth}
                \card{\linewidth}{1.5em}{\faDatabase \, \textbf{Access}}
                    {Your data --- even offline}
            \end{column}
        \end{columns}
    \end{center}
\end{frame}


\begin{frame}
    \frametitle{Confidentiality of your searches}

    Searches can be \textbf{very sensitive}, especially during active incidents.

    \vspace{0.5em}

    \begin{itemize}
        \item The indicators you search for may \textbf{accidentally reveal} sensitive
              information about the infrastructure you protect
        \item You may want to limit the chance that your \textbf{knowledge of an ongoing
              attack} leaks out during an incident
    \end{itemize}

    \vspace{0.5em}

    \alertbox{danger}{Every query is a potential signal}{During an active incident, keep
    sensitive lookups on infrastructure \emph{you} control --- not on a shared instance.}
\end{frame}


\begin{frame}
    \frametitle{Performance \& availability}

    On a shared instance, you are \textbf{at the mercy of the community} for performance
    and response times.

    \vspace{0.5em}

    \begin{itemize}
        \item It would be very unfortunate if your tools could \textbf{not pull the latest
              intel} exactly when you need it most \dots
        \item \dots simply because the MN MISP instance is \textbf{overwhelmed} by an
              unexpected amount of load from the community
        \item A local, synchronised copy keeps your tooling \textbf{fast and independent}
    \end{itemize}

    \vspace{0.5em}

    \alertbox{warning}{When it matters most}{Peak demand on the shared instance often
    coincides with the incidents where you can least afford to wait.}
\end{frame}


\begin{frame}
    \frametitle{The power of your own instance}

    Beyond confidentiality and availability, hosting your own instance unlocks more.

    \vspace{0.5em}

    \begin{center}
        \begin{columns}[T]
            \begin{column}{0.5\textwidth}
                \card{\linewidth}{2.5em}
                    {{\Large\faTools}\hspace{0.3em}\textbf{Extra capability}}
                    {
                        \begin{itemize}
                            \item Functionality reserved for the \textbf{host organisation}
                            \item Administrator-only features
                        \end{itemize}
                    }
            \end{column}
            \begin{column}{0.5\textwidth}
                \card{\linewidth}{2.5em}
                    {{\Large\faDatabase}\hspace{0.3em}\textbf{Own the data}}
                    {
                        \begin{itemize}
                            \item Full access to the data
                            \item Available \textbf{even offline}
                        \end{itemize}
                    }
            \end{column}
        \end{columns}
    \end{center}
\end{frame}


\begin{frame}
    \frametitle{Key takeaways}

    \begin{itemize}
        \item \textbf{Capabilities} --- search, correlate, operationalise and collaborate
              on the MN MISP instance
        \item \textbf{Connecting} --- synchronise in either direction, cross-correlate via
              caching, and filter to taste
        \item \textbf{Considerations} --- your own instance means confidentiality,
              availability, extra capability and offline access
    \end{itemize}

    \vspace{1em}

    \alertbox{info}{Getting started}{Request a sync user from NCIA and decide whether you
    want to \emph{ingest only} or also \emph{share back}.}
\end{frame}
